Discussion Draft v1

### 2020-04-16 doc/Discussion.rmd
changed headers

---
title: "Discussion Draft"
date: ''
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    toc_float: yes
  pdf_document: default
  word_document:
    toc: yes
    toc_depth: '3'
bibliography: refs_Main_Report.bib
---

@@

To place our results in the broader context of meiotic variation we examine three modifier models and two functional and cell physiology models (table X). While there are challenges to fitting models built under different assumptions, we feel it's a useful exercise to highlight any unifying patterns for our specific traits across exsisting models. The three modifier models were built to explain variation in genome wide recombination rates between sexes (heterochiasmy), while the chromosome ocillatory movement (COM) model was built to describe positive interference. This spindle based selection model was developed to explain the results resented in this manuscript. In cases where the models can't be extended to predicting results, we list a 'NA' for the prediction.

# Reversed heterochiasmy direction

@@

# Greater between cell variation

@@

# Typical landscape

@@

# Chromatin Structure

@@

# Evolution of Interference

@@

#Future steps

@@

#References

>>>>

---
title: "Discussion Draft v1"
date: ''
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    toc_float: yes
  pdf_document: default
  word_document:
    toc: yes
    toc_depth: '3'
bibliography: refs_Main_Report.bib
---

@@

To place our results in the broader context of recombination rate variation we examine three modifier models and two functional and cell physiology models (table X). While there are challenges to fitting models built under different assumptions, we feel it's a useful exercise to highlight any unifying patterns for our specific traits across exsisting models. The three modifier models were built to explain variation in genome wide recombination rates between sexes (heterochiasmy), while the chromosome ocillatory movement (COM) model was built to describe positive interference. This spindle based selection model was developed to explain the results resented in this manuscript. In cases where the models can't be extended to predicting results, we list a 'NA' for the prediction.

### Evolution of reversed heterochiasmy direction

@@

### Conservation in sexual dimorphism in between cell variation in crossover number

@@

### Conservation in sex-specific recombination landscape

@@

### Conservation of sex differences in chromatin structure

@@

### Evolution of interference strength in males

@@

### Future steps

@@

# References
